---
title: "Test 1"
output: html_notebook
---

| Test 1                         |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 8:00 PM on Thu Sep 28   | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

**Submit your work to codePost by 8:00 PM. You can only submit it once.**

*Late policy:* For a 10-minute period your work is turned in past 8:00 PM, 
you will lose 25% of the test points. For example, if your work is turned in 
at 8:01 PM, you will lose 25%. After 10 minutes, no late work is accepted.

This is an individual exam. No communication with anyone else is
allowed. However, the exam is open-notes and open-Internet. Observe all
rules as specified on the homeworks as usual. As a reminder, please do
not use Excel to save your CSV file.

You should have received the exam materials (including this file,
`test.Rmd`) from GitHub. Complete the exercises below in order. Before the
time limit has expired, upload the requested files to codePost.

Do not use the `scales` library as it may cause a conflict with `read_csv`.

The data set `data.csv` contains information about bank loans, where each
row corresponds to a specific loan by a specific bank customer. The columns
are as follows:

- `Income` is the customer's annual income (in $);

- `Tenure` is the customer's length of employment at his or her current job;

- `FICO` is the customer's FICO credit score (higher is better);

- `Origination` is the date that the loan was approved;

- `Amount` is the loan amount (in $);
 
- `Grade` is the bank's internal letter grade given to the loan, where A" is 
   the top grade.
   
When done, create a `solution.R` script file and place all R code in it. Be 
sure that it runs stand alone, as this is what I will grade.

# Exercises (add all library commands here)

```{r}


```

## 1 (12 points)

Read and transform `data.csv `into a data frame called `df` so that
`Income` is numeric/double, `Tenure` is factor, `FICO` is integer,
`Origination` is character, `Amount` is integer, and `Grade` is factor.
Treat the empty string, "NA", and "n/a" as missing values. Write `df` to
a csv file called '1.csv'. Be sure to use read_csv with my_col_types set.

```{r}


```

## 2 (4 points)

Remove all rows of `df` having at least one missing value. Write `df` to
a csv file called '2.csv'.

```{r}


```

## 3 (6 points)

Calculate half the median loan amount and save it in a variable called `half_med`.

```{r}


```

## 4 (8 points)

Keep only the rows corresponding to: (i) a positive value of `Income`;
and (ii) a grade which is "A", "B", or "C". Be sure to save the results
back to `df`. Write `df` to a csv file called '4.csv'.

```{r}


```

## 5 (8 points)

Calculate the number of entries in the `FICO` column, which are not
NA's, i.e., the number of entries in `FICO` which contain actual data.
Save the result in `num_not_na`. [Hint: Please do not hard code your
answer, you will lose points. Instead, use R functions to calculate it.]

```{r}


```

## 6 (8 points)

Create box plots of `Income` on `Grade` with `Income` logged. Export the
plot to a file called `graphic.png` with width of 5, height of 4, and 
dpi of 600. [Note: Just do the basic plot. Do not add titles; do not try 
to make the plot beautiful.]

```{r}


```

## 7 (10 points)

In `Tenure`, reorder the levels so that they are in increasing order
based on the amount of tenure, i.e., "0 years" is the first level and
"10+ years" is the last. Save in vector `my_levels`.

```{r}


```

## 8 (10 points)

Create a table called `FICO_table` with `Tenure` in the rows, `Grade` in
the columns, and average FICO score in the table values. Write `FICO_table` 
to a csv file called '8.csv'.

```{r}


```

## 9 (8 points)

Create a new column in `df` called `Date`, which stores the contents of
`Origination` properly converted to the `Date` class. Write `df`to a csv 
file called '9.csv'.

```{r}


```

## 10 (10 points)

Create a new factor column in `df` called `FICO_level` with levels
corresponding to 601-700 (inclusive), 701-800 (inclusive), and 801-900
(inclusive). Name the levels "good", "better", and "best" in that order.
Write `df` to a csv file called '10.csv'.

```{r}


```

## 11 (10 points)

In a new data frame called `best_customers`, store the records of `df`
corresponding to the top-5 customers in terms of highest income, where
these 5 are themselves chosen from the top-100 customers in terms of
highest FICO score. Sort `best_customers` by FICO score in descending
order and then by income in ascending order. [Hint: Make sure to ungroup
`df` first.]  Write `best_customers` to a csv file called '11.csv'.

```{r}


```

## 12 (6 points)

Look at help on the `which(...)` command, and then use it to find the
row indices (or row positions) of all records with `Income` above
$50,000 and `Grade` equal to "A" or "B". Save the row indices in an
object called `row_indices`. 

```{r}


```
